### 2020-10-02 README.Rmd
send readme edits

run_scbi <- TRUE
run_bw <- TRUE
```

@@

Here we re-run the Big Woods model but using the family as the group for comparison. This makes the posterior distributions easier to follow. Also, surprisingly, grouping by family performed just as well as grouping by species (see Allen and Kim 2020).

@@

# b) Recreate Fig5 from Allen (2020): Posterior distributions of selected lambdas
posterior_plots <- plot_posterior_parameters(
  posterior_param = posterior_param_bw,
  sp_to_plot = c("cornaceae", "fagaceae", "hamamelidaceae", "juglandaceae", "lauraceae", "rosaceae", "sapindaceae", "ulmaceae")
)

posterior_plots[["beta_0"]]
posterior_plots[["beta_dbh"]]
posterior_plots[["lambda"]]
```

>>>>

run_scbi <- FALSE
run_bw <- TRUE
```

@@

Here we re-run the Big Woods model but using the family as the group for comparison. This makes the posterior distributions easier to follow. Also, surprisingly, grouping by family performed just as well as grouping by species (see Allen and Kim 2020). First we re-run `create_focal_vs_comp` and `fit_bayesian_model` with the grouping variable as family.

@@

Now the output of `fit_bayesian_model` is passed to `plot_posterior_parameters`.

```{r, eval = run_bw}
# b) Recreate Fig5 from Allen (2020): Posterior distributions of selected lambdas
posterior_plots <- plot_posterior_parameters(
  posterior_param = posterior_param_bw,
  sp_to_plot = c("cornaceae", "fagaceae", "hamamelidaceae", "juglandaceae", "lauraceae", "rosaceae", "sapindaceae", "ulmaceae")
)
```

The output is a list with three plots stored. The element `beta_0` gives the growth intercept, i.e., how fast an individual of each group grows independent of DBH).

```{r, eval = run_bw}
posterior_plots[["beta_0"]]
```

Next `beta_dbh` gives the DBH-growth slope for each group.

```{r, eval = run_bw}
posterior_plots[["beta_dbh"]]
```

Finally `lambda` gives the competition coeffiencts.

```{r, eval = run_bw}
posterior_plots[["lambda"]]
```
